\textit{F1000Research} A studyforrest extension, an annotations of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-07 paper/main.tex
revise cluster tables

\begin{figure*}
  \centering
% \includegraphics[width=0.4\textwidth]{frog.jpg}
  \includegraphics[width=\linewidth]{figures/slicescolorbars}
  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05; cluster corr.; MNI template space).}
  \label{fig:results}
\end{figure*}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast words > no-speech.}
\label{tab:cope1}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
\midrule
4 & 14990 & 0 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
3 & 14469 & 0 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
2 & 1971 & 2.37E-16 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
1 & 217 & 0.00214 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon'').}
\label{tab:cope3}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
\midrule
9 & 7691 & 2.80E-45 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
8 & 5928 & 5.97E-38 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
7 & 479 & 1.13E-06 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
6 & 420 & 4.65E-06 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
5 & 407 & 6.38E-06 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
4 & 294 & 0.000115 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
3 & 121 & 0.0237 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
2 & 117 & 0.0274 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
1 & 115 & 0.0295 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
\bottomrule
\end{tabular}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon'').}
\label{tab:cope5}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
\midrule
4 & 3166 & 2.79E-25 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
3 & 1753 & 7.18E-17 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
2 & 166 & 0.00446 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
1 & 149 & 0.00793 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{figure*}
  \centering
% \includegraphics[width=0.4\textwidth]{frog.jpg}
  \includegraphics[width=\linewidth]{figures/slicescolorbars}
  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected.; MNI template space).}
  \label{fig:results}
\end{figure*}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast words > no-speech. Clusters sorted by voxel size.}
\label{tab:cope1}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
14990 & <.001 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
14469 & <.001 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
1971 & <.001 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon''). Clusters sorted by voxel size.}
\label{tab:cope3}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
7691 & <.001 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
5928 & <.001 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
479 & <.001 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
420 & <.001 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
407 & <.001 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
294 & <.001 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
121 & .024 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
117 & .027 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
115 & .029 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon''). Clusters sorted by voxel size.}
\label{tab:cope5}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3166 & <.001 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
1753 & <.001 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
166 & .004 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
149 & .008 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
\bottomrule
\end{tabular}
\end{table*}
